---
title: "DM Group 30"
output: html_document
date: "2024-03-10"
output:
  pdf_document: default
  html_document: default
editor_options:
  chunk_output_type: inline
---

```{r setup, include=FALSE}
library(readr)
library(RSQLite)
library(dplyr)
library(readxl)
library(openxlsx)
library(ggplot2)
library(scales)
```



```{r my_connection}
my_connection <- RSQLite::dbConnect(RSQLite::SQLite(),"database.db")
```

## Physical Schema
## Create SQL Database Schema Tables
```{r : Create SQL Database Schema Tables}
# Create 'Customers' table.
RSQLite::dbExecute(my_connection,"
  CREATE TABLE IF NOT EXISTS 'Customers' (
    'customer_id' VARCHAR(4) PRIMARY KEY,
    'customer_first_name' VARCHAR(200) NOT NULL,
    'customer_last_name' VARCHAR(200) NOT NULL,
    'customer_gender' VARCHAR(200) NOT NULL,
    'customer_date_of_birth' Date OT NULL,
    'customer_address1' INT NOT NULL,
    'customer_address2' VARCHAR(200) NOT NULL,
    'customer_postcode' VARCHAR(6)NOT NULL,
    'customer_phone_number' VARCHAR(12) NOT NULL,
    'customer_email' VARCHAR(200) NOT NULL,
    'customer_password' VARCHAR(200) NOT NULL);
")

# Create 'Vouchers' table. 
RSQLite::dbExecute(my_connection," 
  CREATE TABLE IF NOT EXISTS 'Vouchers' (
    'voucher_id' VARCHAR(5) PRIMARY KEY ,
    'voucher_name' VARCHAR(200) NOT NULL,
    'voucher_value' INT Not NULL,
    'voucher_starts_date' DATE Not NULL,
    'voucher_expiry_date' DATE Not NULL);
")

# Create 'Suppliers' table. 
RSQLite::dbExecute(my_connection,"
  CREATE TABLE IF NOT EXISTS 'Suppliers' (
    'supplier_id' VARCHAR(7) PRIMARY KEY,
    'supplier_name' VARCHAR(200) NOT NULL,
    'supplier_phone_number' VARCHAR(12) NOT NULL,
    'supplier_email' VARCHAR(200) NOT NULL,
    'supplier_password' VARCHAR(200) NOT NULL,
    'supplier_address1' INT NOT NULL,
    'supplier_address2' VARCHAR(200) NOT NULL,
    'supplier_postcode' VARCHAR(6) NOT NULL,
    'supplier_sort_code' VARCHAR(10) NOT NULL,
    'supplier_account_name' VARCHAR(200) NOT NULL,
    'supplier_account_number' VARCHAR(16) NOT NULL);
")

# Create 'Categories' table.  
RSQLite::dbExecute(my_connection,"
  CREATE TABLE IF NOT EXISTS 'Categories' (
    'parent_category_id' VARCHAR(3),
    'category_id' VARCHAR(5) PRIMARY KEY,
    'category_name' VARCHAR(200) NOT NULL,
    'category_description' TEXT,
    FOREIGN KEY ('parent_category_id') REFERENCES Categories ('category_id'));
")

# Create 'Cards' table. 
RSQLite::dbExecute(my_connection," 
  CREATE TABLE IF NOT EXISTS 'Cards'(
    'card_number' INT PRIMARY KEY,
    'card_holder_first_name' VARCHAR(200) NOT NULL,
    'card_holder_last_name' VARCHAR(200) NOT NULL,
    'card_types' VARCHAR(200) NOT NULL,
    'card_cvv' INT NOT NULL,
    'card_expiry_date' DATE NOT NULL,
    'customer_id' VARCHAR(4),
    FOREIGN KEY ('customer_id') REFERENCES Customers('customer_id'));
")

# Create 'Products' table.
RSQLite::dbExecute(my_connection,"
  CREATE TABLE IF NOT EXISTS 'Products' (
    'product_id' VARCHAR(7) PRIMARY KEY,
    'product_name' VARCHAR(200) NOT NULL,
    'product_price' DOUBLE NOT NULL,
    'product_quantity' INT NOT NULL,
    'product_description' TEXT,
    'supplier_id' VARCHAR(7),
    'category_id' VARCHAR(5),
    FOREIGN KEY ('supplier_id') REFERENCES Suppliers('supplier_id'),
    FOREIGN KEY ('category_id') REFERENCES Categories('category_id'));
")

# Create 'Orders_Details' table.
RSQLite::dbExecute(my_connection,"
  CREATE TABLE IF NOT EXISTS 'Orders_Details' (
    'order_id' VARCHAR(5) PRIMARY KEY,
    'order_date' DATE NOT NULL,
    'order_status' VARCHAR(200) NOT NULL,
    'recipient_first_name' VARCHAR(200) NOT NULL,
    'recipient_last_name' VARCHAR(200) NOT NULL,
    'recipient_phone_number' VARCHAR(200) NOT NULL,
    'delivery_address1' INT NOT NULL,
    'delivery_address2' VARCHAR(200) NOT NULL,
    'delivery_postcode' VARCHAR(6) NOT NULL,
    'delivery_type' VARCHAR(200) NOT NULL,
    'expected_delivery_date' DATE,
    'delivered_date' DATE,
    'delivery_instructions' TEXT,
    'voucher_id' VARCHAR(5),
    FOREIGN KEY ('voucher_id') REFERENCES Vouchers ('voucher_id'));
")

# Create 'Order_Relationship' table.
RSQLite::dbExecute(my_connection,"
  CREATE TABLE IF NOT EXISTS 'Order_Relationship' (
    'order_id' VARCHAR(5),
    'customer_id' VARCHAR(4),
    'product_id' VARCHAR(6),
    'order_quantity' INT,
    PRIMARY KEY (order_id,customer_id,product_id),
    FOREIGN KEY ('order_id') REFERENCES Order_Details ('order_id')
    FOREIGN KEY ('customer_id') REFERENCES Customers('customer_id'),
    FOREIGN KEY ('product_id') REFERENCES Products('product_id'));
")

# Create 'Transactions' table.
RSQLite::dbExecute(my_connection,"
  CREATE TABLE IF NOT EXISTS 'Transactions' (
    'transaction_id' VARCHAR(5) PRIMARY KEY,
    'transaction_date' DATE NOT NULL,
    'transaction_status' VARCHAR(200) NOT NULL,
    'card_number' VARCHAR(200) NOT NULL,
    'order_id' VARCHAR(5) NOT NULL,
    FOREIGN KEY ('card_number') REFERENCES Cards ('card_number'),
    FOREIGN KEY ('order_id') REFERENCES Order_Details ('order_id'));
")

```

## Load Synthetic Data

```{r : Load Synthetic Data}
# Load the 'Customers' data.
Customers <- readr::read_csv('old_data/Customers.csv')

# Load the 'Vouchers' data.
Vouchers <- readr::read_csv('old_data/Vouchers.csv')
  
# Load the 'Suppliers' data.
Suppliers <- readr::read_csv('old_data/Suppliers.csv')

  
# Load the 'Categories' data.
Categories <- readr::read_csv('old_data/Categories.csv')

# Load the 'Cards' data.
Cards <- readr::read_csv('old_data/Cards.csv')

# Load the 'Products' data.
Products <- readr::read_csv('old_data/Products.csv')

# Load the 'Order_Details' data.
Order_Details <- readr::read_csv('old_data/Order_Details.csv')

# Load the 'Order_Relationship' data.
Order_Relationship <- readr::read_csv('old_data/Order_Relationship.csv')

# Load the 'Transactions' data.
Transactions <- readr::read_csv('old_data/Transactions.csv')

```

## Data Validation for Quality and Integrity in Dataset

Alex
Customers
- 'customer_id'
- 'customer_postcode'
- 'customer_phone_number'
- 'customer_email' 

Products 
- 'product_id'

Categories
- 'parent_category_id'
- 'category_id'

Order Details
- 'order_id'
- 'recipient_phone_number'
- 'delivery_postcode'

Wiran
Suppliers
- 'supplier_id'
- 'supplier_phone_number'	
- 'supplier_email'
- 'supplier_postcode'
- 'supplier_sort_code' 
- 'supplier_account_number'

Cards 
- 'card_number'
- 'card_cvv'

Vouchers
- 'voucher_id'

Transaction 
- 'transaction_id'

### Check the format of Customers.

```{r Data Validation for Quality and Integrity : Customers}
# Check the format of the 'customer_id' column.
# State the format.
format_check_customer_id <- grep('^A0[0 - 9][0 - 9]$', Customers$customer_id)

# If any value doesn't match the desired format, print the problematic values.
if (length(format_check_customer_id) > 0) {
  cat('customer_id column contains values not matching the format:\n')
  cat(Customers$customer_id[format_check_customer_id], '\n')
} else {
  cat('All values in the customer_id column match the format.\n')
}

# Check the result whether the format is correct or not. 
result_check_customer_id <- ifelse(length(format_check_customer_id) > 0, 'false', 'true')
result_check_customer_id

# Check the format of the 'customer_postcode' column.
# State the format.
format_check_customer_postcode <- grep('^CV1[0 - 9][A - Z]{2}$', Customers$customer_postcode)

# If any value doesn't match the desired format, print the problematic values.
if (length(format_check_customer_postcode) > 0) {
  cat('customer_postcode column contains values not matching the format:\n')
  cat(Customers$customer_postcode[format_check_customer_postcode], '\n')
} else {
  cat('All values in the customer_postcode column match the format.\n')
}

# Check the result whether the format is correct or not. 
result_check_customer_postcode <- ifelse(length(format_check_customer_postcode) > 0, 'false', 'true')
result_check_customer_postcode

# Check the format of the 'customer_phone_number' column.
# State the format.
format_check_customer_phone_number <- grep('^[0 - 9]{3} - [0 - 9]{3} - [0 - 9]{4}$', Customers$customer_phone_number)

# If any value doesn't match the desired format, print the problematic values.
if (length(format_check_customer_phone_number) > 0) {
  cat('customer_phone_number column contains values not matching the format:\n')
  cat(Customers$customer_phone_number[format_check_customer_phone_number], '\n')
} else {
  cat('All values in the customer_phone_number column match the format.\n')
}

# Check the result whether the format is correct or not. 
format_check_customer_phone_number <- ifelse(length(format_check_customer_phone_number) > 0, 'false', 'true')
format_check_customer_phone_number

# Check the format of the 'customer_email' column.
# State the format.
format_check_customer_email <- grep('^[0 - 9]{3} - [0 - 9]{3} - [0 - 9]{4}$', Customers$customer_email)

# If any value doesn't match the desired format, print the problematic values.
if (length(format_check_customer_email) > 0) {
  cat('customer_email column contains values not matching the format:\n')
  cat(Customers$customer_email[format_check_customer_email], '\n')
} else {
  cat('All values in the customer_email column match the format.\n')
}

# Check the result whether the format is correct or not. 
format_check_customer_email <- ifelse(length(format_check_customer_email) > 0, 'false', 'true')
format_check_customer_email
```



## Insert the Initial Dataset into Schema Tables

```{r : Insert the Initial Dataset into Schema Tables}
# Insert the 'Customers' data.
RSQLite::dbWriteTable(my_connection,'Customers', Customers, append = TRUE)

# Insert the 'Vouchers' data.
RSQLite::dbWriteTable(my_connection,'Vouchers', Vouchers, append = TRUE)

# Insert the 'Suppliers' data.
RSQLite::dbWriteTable(my_connection,'Suppliers', Suppliers, append = TRUE)

# Insert the 'Categories' data.
RSQLite::dbWriteTable(my_connection,'Categories', Categories, append = TRUE)

# Insert the 'Cards' data.
RSQLite::dbWriteTable(my_connection,'Cards', Cards, append = TRUE)

# Insert the 'Products' data.
RSQLite::dbWriteTable(my_connection,'Products', Products, append = TRUE)

# Insert the 'Order_Details' data.
RSQLite::dbWriteTable(my_connection,'Order_Details', Order_Details, append = TRUE)

# Insert the 'Order_Relationship' data.
RSQLite::dbWriteTable(my_connection,'Order_Relationship', Order_Relationship, append = TRUE)

# Insert the 'Transactions' data.
RSQLite::dbWriteTable(my_connection,'Transactions', Transactions, append = TRUE)
```

## Load and Append New Data into Schema Tables

```{r : Load and Append New Data into Schema Tables}
Order_Details_new <- read_excel('new_data/New_order.xlsx',sheet = 'Order_Details')
Order_Relationship_new <- read_excel('new_data/New_order.xlsx',sheet = 'Order_Relationships')

RSQLite::dbWriteTable(my_connection,'Order_Details',Order_Details_new , append = TRUE)
RSQLite::dbWriteTable(my_connection,'Order_Relationship', Order_Relationship_new, append = TRUE)
```

## Data Validation for Quality and Integrity in New Dataset
```{sql connection=my_connection}
PRAGMA table_info('Customers');
```

## Analysis
### Top 10 Products Based on Quantity

```{r}
top_10_product_based_on_quantity <- function() {
  return(
          RSQLite::dbGetQuery(my_connection,'
            SELECT p.product_id, p.product_name,
                   SUM(or_rel.order_quantity) AS total_quantity_sold
            FROM Products p
            JOIN Order_Relationship or_rel ON p.product_id = or_rel.product_id
            GROUP BY p.product_id, p.product_name
            ORDER BY total_quantity_sold DESC
            LIMIT 10;
          ')
  )
}
```

### Top 10 Products Based on Revenue

```{r}
top_10_product_based_on_revenue <- function() {
    return(
            RSQLite::dbGetQuery(my_connection,'
              SELECT p.product_id, p.product_name,
                     SUM(or_rel.order_quantity * p.product_price) AS total_revenue
              FROM Products p
              JOIN Order_Relationship or_rel ON p.product_id = or_rel.product_id
              GROUP BY p.product_id, p.product_name
              ORDER BY total_revenue DESC
              LIMIT 10;
              ')
    )
}
```

### Top 3 Categories Based on Quantity

```{r}
top_3_categories_based_on_quantity <- function() {
    return(
            RSQLite::dbGetQuery(my_connection,'
              SELECT c.category_id, c.category_name,
                     SUM(or_rel.order_quantity) AS total_quantity_sold
              FROM Categories c
              JOIN Products p ON c.category_id = p.category_id
              JOIN Order_Relationship or_rel ON p.product_id = or_rel.product_id
              GROUP BY c.category_id, c.category_name
              ORDER BY total_quantity_sold DESC
              LIMIT 3;
            ')
    )
}
```

### Top 3 Categories Based on Quantity

```{r}
top_3_categories_based_on_revenue <- function() {
    return(
            RSQLite::dbGetQuery(my_connection,'
              SELECT c.category_id, c.category_name,
                     SUM(or_rel.order_quantity * p.product_price) AS total_revenue_generated
              FROM Categories c
              JOIN Products p ON c.category_id = p.category_id
              JOIN Order_Relationship or_rel ON p.product_id = or_rel.product_id
              GROUP BY c.category_id, c.category_name
              ORDER BY total_revenue_generated DESC
              LIMIT 3;
            ')
    )
}

```

### Top 10 Custmers

```{r}
top_10_customers_based_on_the_total_amount_spent_on_orders <- function() {
    return(
            RSQLite::dbGetQuery(my_connection,'
              SELECT c.customer_id, c.customer_first_name, c.customer_last_name,
                     SUM(p.product_price * or_rel.order_quantity) AS total_amount_spent
              FROM Customers c
              JOIN Order_Relationship or_rel ON c.customer_id = or_rel.customer_id
              JOIN Products p ON or_rel.product_id = p.product_id
              JOIN Transactions t ON or_rel.order_id = t.order_id
              GROUP BY c.customer_id, c.customer_first_name, c.customer_last_name
              ORDER BY total_amount_spent DESC
              LIMIT 10;
            ')
    )
}
```

### Most Popular Delivery Type

```{r}
the_most_popular_delivery_type_based_on_the_number_of_orders <- function() {
    return(
            RSQLite::dbGetQuery(my_connection,'
              SELECT delivery_type, COUNT(*) AS num_orders
              FROM Order_Details
              WHERE delivery_type IS NOT NULL
              GROUP BY delivery_type
              ORDER BY num_orders DESC
              LIMIT 1;
            ')
    )
}
```

### Products needed for Inventory Replenishment (Quantity Less Than 50 Items)

```{r}
products_that_are_running_low <- function() {
    return(
            RSQLite::dbGetQuery(my_connection,'
              SELECT *
              FROM Products
              WHERE product_quantity < 50;
            ')
    )
}
```

### Supplier Performance

```{r}
supplier_performance_based_on_the_number_of_products_supplied <- function() {
    return(
            RSQLite::dbGetQuery(my_connection,'
              SELECT 
                  s.supplier_id,
                  s.supplier_name,
                  COUNT(DISTINCT p.product_id) AS num_products_supplied
              FROM 
                  Suppliers s
              LEFT JOIN 
                  Products p ON s.supplier_id = p.supplier_id
              GROUP BY 
                  s.supplier_id, s.supplier_name;
            ')
    )
}
```

## Analyze the distribution of customers by gender and age groups
```{r by gender}
analyzing_distribution_of_customers_by_gender <- function() {
    return(
            RSQLite::dbGetQuery(my_connection,'
              SELECT 
                  customer_gender,
                  COUNT(*) AS customer_count
              FROM 
                  Customers
              GROUP BY 
                  customer_gender;
            ')
    )
}
```

```{r by age groups}
analyzing_distribution_of_customers_by_age_group <- function() {
    return(
            RSQLite::dbGetQuery(my_connection,"
              SELECT 
                  CASE
                      WHEN strftime('%Y', 'now') - strftime('%Y', formatted_date_of_birth) - 
                           (strftime('%m-%d', 'now') < strftime('%m-%d', formatted_date_of_birth)) BETWEEN 0 AND 18 THEN '0-18'
                      WHEN strftime('%Y', 'now') - strftime('%Y', formatted_date_of_birth) - 
                           (strftime('%m-%d', 'now') < strftime('%m-%d', formatted_date_of_birth)) BETWEEN 19 AND 30 THEN '19-30'
                      WHEN strftime('%Y', 'now') - strftime('%Y', formatted_date_of_birth) - 
                           (strftime('%m-%d', 'now') < strftime('%m-%d', formatted_date_of_birth)) BETWEEN 31 AND 45 THEN '31-45'
                      WHEN strftime('%Y', 'now') - strftime('%Y', formatted_date_of_birth) - 
                           (strftime('%m-%d', 'now') < strftime('%m-%d', formatted_date_of_birth)) BETWEEN 46 AND 60 THEN '46-60'
                      ELSE '61+'
                  END AS age_group,
                  COUNT(*) AS num_customers
              FROM 
                  (SELECT 
                      strftime('%Y-%m-%d', substr(customer_date_of_birth, 7) || '-' || substr(customer_date_of_birth, 4, 2) || '-' || substr(customer_date_of_birth, 1, 2)) AS formatted_date_of_birth
                  FROM 
                      Customers) AS converted_dates
              GROUP BY 
                  age_group
              ORDER BY 
                  MIN(strftime('%Y', 'now') - strftime('%Y', formatted_date_of_birth) - 
                      (strftime('%m-%d', 'now') < strftime('%m-%d', formatted_date_of_birth)));
            ")
    )
}
```

# write the analysis results into excel
```{r}
# Execute the functions and store results
result_top_10_product_based_on_quantity <- top_10_product_based_on_quantity()
result_top_10_product_based_on_revenue <- top_10_product_based_on_revenue()
result_top_3_categories_based_on_quantity <- top_3_categories_based_on_quantity()
result_top_3_categories_based_on_revenue <- top_3_categories_based_on_revenue()
result_top_10_customers_based_on_the_total_amount_spent_on_orders <- top_10_customers_based_on_the_total_amount_spent_on_orders()
result_the_most_popular_delivery_type_based_on_the_number_of_orders <- the_most_popular_delivery_type_based_on_the_number_of_orders()
result_products_that_are_running_low <- products_that_are_running_low()
result_supplier_performance_based_on_the_number_of_products_supplied <- supplier_performance_based_on_the_number_of_products_supplied()
result_analyzing_distribution_of_customers_by_gender <- analyzing_distribution_of_customers_by_gender()
result_analyzing_distribution_of_customers_by_age_group <- analyzing_distribution_of_customers_by_age_group()

# Create a new workbook
wb <- openxlsx::createWorkbook()

# Add sheets to the workbook
openxlsx::addWorksheet(wb, 'Top 10 Products Quantity')
openxlsx::addWorksheet(wb, 'Top 10 Products Revenue')
openxlsx::addWorksheet(wb, 'Top 3 Categories Quantity')
openxlsx::addWorksheet(wb, 'Top 3 Categories Revenue')
openxlsx::addWorksheet(wb, 'Top 10 Customers Spent')
openxlsx::addWorksheet(wb, 'Popular Delivery Type')
openxlsx::addWorksheet(wb, 'Products Running Low')
openxlsx::addWorksheet(wb, 'Supplier Performance')
openxlsx::addWorksheet(wb, 'Customer Distribution by Gender')
openxlsx::addWorksheet(wb, 'Customer Age Distribution')

# Write results to sheets
openxlsx::writeData(wb, 'Top 10 Products Quantity', result_top_10_product_based_on_quantity)
openxlsx::writeData(wb, 'Top 10 Products Revenue', result_top_10_product_based_on_revenue)
openxlsx::writeData(wb, 'Top 3 Categories Quantity', result_top_3_categories_based_on_quantity)
openxlsx::writeData(wb, 'Top 3 Categories Revenue', result_top_3_categories_based_on_revenue)
openxlsx::writeData(wb, 'Top 10 Customers Spent', result_top_10_customers_based_on_the_total_amount_spent_on_orders)
openxlsx::writeData(wb, 'Popular Delivery Type', result_the_most_popular_delivery_type_based_on_the_number_of_orders)
openxlsx::writeData(wb, 'Products Running Low', result_products_that_are_running_low)
openxlsx::writeData(wb, 'Supplier Performance', result_supplier_performance_based_on_the_number_of_products_supplied)
openxlsx::writeData(wb, 'Customer Distribution by Gender', result_analyzing_distribution_of_customers_by_gender)
openxlsx::writeData(wb, 'Customer Age Distribution', result_analyzing_distribution_of_customers_by_age_group)

# Save the workbook
openxlsx::saveWorkbook(wb, 'analysis_results.xlsx', overwrite = TRUE)
```

```{r}
sales <- dbGetQuery(my_connection, '
  SELECT product_id, SUM(order_quantity) AS total_sales
  FROM Order_Relationship
  GROUP BY product_id
  ORDER BY total_sales DESC
  LIMIT 1
')

top_product_id <- sales$product_id[1]

product_sales <- dbGetQuery(my_connection, '
  SELECT DATE(datetime(od.order_date, 'unixepoch')) AS order_date, or_rel.order_quantity
  FROM Order_Details od
  INNER JOIN Order_Relationship or_rel ON od.order_id = or_rel.order_id
  WHERE or_rel.product_id = ?
', params = list(top_product_id))

product_sales$order_date <- as.Date(product_sales$order_date)

ggplot(product_sales, aes(x = order_date, y = order_quantity)) +
  geom_line() +
  labs(title = paste('Sales Trend of Product', top_product_id),
       x = 'Date',
       y = 'Sales Quantity')
```
# Customer:
## gender pie chart
```{r}
gender_counts_df <- as.data.frame(result_analyzing_distribution_of_customers_by_gender)
names(gender_counts_df) <- c('Gender', 'Count')

gender_counts_df$Percent <- gender_counts_df$Count / sum(gender_counts_df$Count) * 100


( gender_pie_chart <- ggplot(gender_counts_df, aes(x = "", y = Percent, fill = Gender)) +
  geom_bar(stat = 'identity') +
  coord_polar('y', start = 0) +
  geom_text(aes(label = paste(round(Percent), '%')), position = position_stack(vjust = 0.5)) +
  labs(title = 'Customer Gender Distribution', fill = 'Gender') +
  theme_minimal() +
  theme(legend.position = 'right') +
  theme_void() +
  scale_fill_discrete(name = 'Gender') )
```

## age violin chart
```{r}
age_data <- RSQLite::dbGetQuery(my_connection, "
    SELECT strftime('%Y', 'now') - strftime('%Y', formatted_date_of_birth) - 
                           (strftime('%m-%d', 'now') < strftime('%m-%d', formatted_date_of_birth))  AS age
    FROM 
                  (SELECT 
                      strftime('%Y-%m-%d', substr(customer_date_of_birth, 7) || '-' || substr(customer_date_of_birth, 4, 2) || '-' || substr(customer_date_of_birth, 1, 2)) AS formatted_date_of_birth
                  FROM 
                      Customers) AS converted_dates
")

age_data$age_group <- cut(age_data$age, breaks = c(0, 30,  Inf),
                          labels = c('0-30', '31+'))

# violin
( age_violin_chart <- ggplot(age_data, aes(x = age_group, y = age)) +
  geom_violin() +
  labs(title = 'Distribution of Customer Age by Age Group',
       x = 'Age Group', y = 'Age') +
  theme_minimal() )
```

# Product
# product price distribution based on parent category 
```{r}
query <- '
  SELECT pc.category_name AS parent_category_name, p.product_price
  FROM Products p
  JOIN Categories c ON p.category_id = c.category_id
  JOIN Categories pc ON c.parent_category_id = pc.category_id;
'
product_price_data <- RSQLite::dbGetQuery(my_connection, query)

( product_price_distribution <- ggplot(product_price_data, aes(x = parent_category_name, y = product_price)) +
  geom_violin(trim = FALSE) + 
  labs(title = 'Product Price Distribution Based on Parent Category', x = 'Parent Category', y = 'Product Price') +
  theme_minimal() )
```

## top 3 category based on sales
```{r}
( top_3_category_based_on_sales <- ggplot(result_top_3_categories_based_on_revenue, aes(x = category_name, y = total_revenue_generated)) +
  geom_bar(stat = 'summary', fun = 'mean', fill = 'skyblue', color = 'black') +
  labs(title = 'top 3 category based on sales',
       x = 'category name',
       y = 'total sales generated') +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) )
```

## top 10 products based on sales
```{r}
( top_10_products_based_on_sales <- ggplot(result_top_10_product_based_on_revenue, aes(x = product_name, y = total_revenue)) +
  geom_bar(stat = 'summary', fun = 'mean', fill = 'skyblue', color = 'black') +
  labs(title = 'top 10 products based on sales',
       x = 'product name',
       y = 'total sales generated') +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) )
```

# Cards
## the total of customers on number of cards
```{r}
number_of_customers_based_on_cards <- RSQLite::dbGetQuery(my_connection, '
  SELECT
      num_cards,
      COUNT(*) AS num_customers
  FROM (
      SELECT
          customer_id,
          COUNT(*) AS num_cards
      FROM
          Cards
      GROUP BY
          customer_id
  ) AS card_counts
  GROUP BY
      num_cards
  ORDER BY
      num_cards;
')

( total_customers_on_number_of_cards <- ggplot(number_of_customers_based_on_cards, aes(x = num_cards, y = num_customers)) +
  geom_bar(stat = 'summary', fun = 'mean', fill = 'skyblue', color = 'black') +
  labs(title = 'the total of customers on number of cards',
       x = 'number of cards',
       y = 'the total of customers') +
  theme_minimal() )
```

# Suppliers
## top 3 suppliers
```{r}
( top_3_suppliers <- ggplot(result_supplier_performance_based_on_the_number_of_products_supplied[1:3,], aes(x = supplier_name, y = num_products_supplied)) +
  geom_bar(stat = 'summary', fun = 'mean', fill = 'skyblue', color = 'black') +
  labs(title = 'top 3 suppliers',
       x = 'supplier_name',
       y = 'number of products supplied') +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) )
```

# Order_details
## time series of order daily for 3 months
```{r}
time_series <- RSQLite::dbGetQuery(my_connection, "
    SELECT 
        strftime('%Y-%m-%d',datetime(order_date, 'unixepoch')) AS Order_Date,
        COUNT(order_id) AS order_amount
    FROM 
        Order_Details
    GROUP BY 
        order_date
    ORDER BY 
        order_date;
")

time_series$Order_Date <- as.POSIXct(time_series$Order_Date, origin = '1970-01-01')

( time_series_of_order_daily <- ggplot(time_series, aes(x = Order_Date, y = order_amount)) +
  geom_line() +
  labs(title = 'time series of order daily for 3 months',
       x = 'order date',
       y = 'order amount')+
  theme_minimal()+
  scale_x_datetime(date_labels = '%Y-%m-%d') )
```

# Vouchers
## 5 most used voucher from orde
```{r}
# Calculate the usage count of each voucher
voucher_usage <- RSQLite::dbGetQuery(my_connection, '
  SELECT voucher_id, COUNT(*) AS usage_count
  FROM Order_Details
  WHERE voucher_id IS NOT NULL
  GROUP BY voucher_id
  ORDER BY usage_count DESC
  LIMIT 5
')

# Use mutate to calculate row number and mark the top two most used vouchers as 'highlight'
voucher_usage <- voucher_usage %>%
  mutate(highlight = ifelse(row_number() <= 2, 'highlight', 'normal'))

# Get the names of vouchers
voucher_names <- RSQLite::dbGetQuery(my_connection, '
  SELECT voucher_id, voucher_name
  FROM Vouchers
')

# Merge voucher usage count and names
voucher_usage <- merge(voucher_usage, voucher_names, by = 'voucher_id')

# Draw the bar chart
(most_used_vouchers_from_order <- ggplot(voucher_usage, aes(x = reorder(voucher_name, -usage_count), y = usage_count, fill = highlight)) +
  geom_bar(stat = 'identity') +
  scale_fill_manual(values = c('highlight' = 'pink', 'normal' = 'skyblue')) +
  labs(title = 'Top 5 Most Used Vouchers',
       x = 'Voucher',
       y = 'Usage Count') +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) )

```

# save each plot as a png file
```{r}
this_filename_date <- as.character(Sys.Date())
this_filename_time <- as.character(format(Sys.time(), format = '%H_%M'))
ggsave(paste0('analysis_graphs/gender_pie_chart_',this_filename_date,'_',this_filename_time,'.png'), plot = gender_pie_chart, width = 8, height = 6, units = 'in')
ggsave(paste0('analysis_graphs/age_violin_chart_',this_filename_date,'_',this_filename_time,'.png'), plot = age_violin_chart, width = 8, height = 6, units = 'in')
ggsave(paste0('analysis_graphs/product_price_distribution_',this_filename_date,'_',this_filename_time,'.png'), plot = product_price_distribution, width = 8, height = 6, units = 'in')
ggsave(paste0('analysis_graphs/top_3_category_based_on_sales_',this_filename_date,'_',this_filename_time,'.png'), plot = top_3_category_based_on_sales, width = 8, height = 6, units = 'in')
ggsave(paste0('analysis_graphs/top_10_products_based_on_sales_',this_filename_date,'_',this_filename_time,'.png'), plot = top_10_products_based_on_sales, width = 8, height = 6, units = 'in')
ggsave(paste0('analysis_graphs/total_customers_on_number_of_cards_',this_filename_date,'_',this_filename_time,'.png'), plot = total_customers_on_number_of_cards, width = 8, height = 6, units = 'in')
ggsave(paste0('analysis_graphs/top_3_suppliers_',this_filename_date,'_',this_filename_time,'.png'), plot = top_3_suppliers, width = 8, height = 6, units = 'in')
ggsave(paste0('analysis_graphs/time_series_of_order_daily_',this_filename_date,'_',this_filename_time,'.png'), plot = time_series_of_order_daily, width = 8, height = 6, units = 'in')
ggsave(paste0('analysis_graphs/most_used_vouchers_from_order_',this_filename_date,'_',this_filename_time,'.png'), plot = most_used_vouchers_from_order, width = 8, height = 6, units = 'in')

```







